Geographically aware estimates of remotely sensed water properties for Chesapeake Bay

### 2022-11-18 manuscript/manuscript.tex
cite zenodo

All code for data processing, model fitting, and model evaluation is available at Stachelek et al. (2023a) the pipeline for which is shown in Figure 1. All data used in the study are available in \cite{stachelekjemmachesapeake}.

>>>>

All code for data processing, model fitting, and model evaluation for the pipeline shown in Figure 1 is available in \cite{jemma_stachelek_2022_7332559}. All data used in the study are available in \cite{stachelekjemmachesapeake}.
